### 2022-11-15 NSF2022/Description/broaderimpacts.tex
ed imp done

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
undergraduate researchers (URs) per year at Fordham University. PI Ryham
has worked side-by-side and published with undergraduate
coauthors~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}. He is presently
mentoring a Clare Boothe Luce Scholar on mathematical analysis of trends
in election redistricting. With another Fordham supported UR, he is
finishing a paper on a closed-form energy density for translationally
invariant bilayers. Based on these experiences, we have outlined three
projects for the present proposal.
\todo[inline]{Rolf: Can you update this?}
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language

\item Use machine learning to post-process data from the granules self-assembly

\item Mathematically investigate self-assembly in the zero-screen-length limit
\end{enumerate}
The UR support is for eight summer weeks. In addition to collaborating
with PI Ryham, they will have tutorials and receive training in
mathematical writing and presentation. The URs will have desks and
meeting room in a recently completed collaboration space built for the
Mathematics Department. As a condition of support, they will be required
to write a summary report and give a presentation in the university's
undergraduate research symposium. PI Ryham will encourage the URs to
participate in a national conference.

To meaningfully engage the community, the PIs will prioritize students
coming from underrepresented groups and specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences. PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team.

>>>>

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers
(URs) per year at Fordham University---for eight summer weeks.
The UR will collaborate directly with PI Ryham,
receive tutorials e.g., numerical methods,
and be guided on mathematical writing and presentation.
Fordham Mathematics recently completed a collaboration studio 
purpose-built for UR support.
Work products include a summary manuscript,
a presentation in the Fordham Undergraduate Research Symposium
and departmental seminars, and participation in a national conference.
We have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language 
\item Use machine learning to post-process data of granule dynamics
\item Investigate geometrical self-assembly and generate visualizations
\end{enumerate}
PI Ryham has worked side-by-side with dozens of
undergraduates and high-schoolers in
supported summer research, Girls in Science Technology and Mathematics,
and the Clare Boothe Luce Scholarship program
and the activity benefited their careers in
machine learning, water resources engineering, threat detection,
and the NYC Department of Education.
Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on election redistricting.
The PI is finishing works on the energy density lipid  bilayers
with a recently graduated UR, now working at Raytheon Technologies.
His published works~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16} include
four undegraduate coauthors.

To increase the participation of women,
persons with disabilities and underrepresented minorities in STEM,
the PIs will specifically target students
whose socio-economic background prevents them from participating in
out-of-state research experiences.
The inclusion objective will be aided by the fact that  
Fordham's class of 2026 weighs in with 63 \% women
and more than 46 \% domestic students of color. 
PI Ryham will solicit applicants from
Fordham University's Collegiate Science and Technology Entry Program.
Students from the Bronx High School of Science (PI Ryham) and Newark
Science Park High School (PI Young) will also be encouraged to join the
research team.
